# Figures

(ref:figure1) Location of the boundaries of the mainland inlet localities, one exploratory site and the five spatial areas (S~1~-S~5~) of the stratified random survey design. The three depths strata (RD~1~-RD~3~) are colour-coded and nested within each of the five spatial strata. Outline of groundfish management areas (inset).

```{r figure1, fig.cap='(ref:figure1)', warning=FALSE, echo=FALSE, dpi=550, out.width = "415px", out.height = "510px", fig.align="center"}
      img <- paste(basepath,'figure1x.png',sep='') 
      knitr::include_graphics(img)
```
\clearpage

(ref:figure2) Start locations of survey sets in `r yr` conducted in the stratified random survey areas S~1~ through S~5~ (red markers) and in the exploratory area (purple markers).  The camera sets are represented by yellow markers.  Set numbers in red font represent sets that released Pacific spiny dogfish with pop-off satellite tags for Alaska Auke Bay Laboratories (ABL).

```{r figure2, fig.cap='(ref:figure2)', out.width = "490px", out.height = "386px", fig.align="center", warning=FALSE, echo=FALSE, message=FALSE, error=FALSE}
      img <- paste(basepath,'figure2x.png',sep='') 
      knitr::include_graphics(img)
```
\clearpage

(ref:figure3) Location of the traditional survey sets within the mainland inlet localities for the `r yr` survey.

```{r figure3, fig.cap='(ref:figure3)', out.width = "410px", out.height = "530px", fig.align="center", warning=FALSE, echo=FALSE, message=FALSE, error=FALSE}
      img <- paste(basepath,'figure3.png',sep='') 
      knitr::include_graphics(img)
```
\clearpage

(ref:figure4)  Image of the 35.66 meter F/V `r boat` used for the `r yr` sablefish research and assessment survey. Photo credit: `r boat` Facebook page.

```{r figure4, fig.cap='(ref:figure4)', out.width = "480px", out.height = "360px", echo=FALSE, fig.align="center", warning=FALSE}
      img  <- paste(basepath,'figure4.png',sep="") 
      knitr::include_graphics(img)
```
\clearpage

(ref:figure5)  Trap gear elements consisting of 25 baited traps snapped to beckets along a groundline (A).  Trap elements (B).

```{r figure5, fig.cap='(ref:figure5)', out.width = "370px", out.height = "610px", echo=FALSE, fig.align="center", warning=FALSE}
      img  <- paste(basepath,'figure5.png',sep="") 
      knitr::include_graphics(img)
```
\clearpage


```{r figure6prep, echo=FALSE, out.width = "400px",  fig.align = "center", warning=FALSE}

    #   results='asis',echo=FALSE,include=FALSE,warning=FALSE,message = FALSE,error= FALSE
    #png(paste(basepath,'figure6.png',sep=''), width = 475, height = 684)  # write png to folder 

    #   query----------raw survey datafile for Landmark fisheries----------------
    landmrk <- paste("select fecCPUE.TRIP_ID, fecCPUE.VESSEL_ID, fecCPUE.SUFFIX, ",                                  
                     "fecCPUE.CAPTAIN_ID, fecCPUE.FISHING_EVENT_ID, fecCPUE.FE_MAJOR_LEVEL_ID,",
                     "fecCPUE.SET_YEAR,   fecCPUE.SET_MONTH, fecCPUE.SET_DAY, ",                               
                     "fecCPUE.SET_TIME,   fecCPUE.DURATION_MINUTES, fecCPUE.SABLE_DEPTH_GROUP, ",                     
                     "fecCPUE.SABLE_AREA_GROUP, fecCPUE.SABLE_SET_TYPE, ", 
                     "fecCPUE.GROUPING_CODE, fecCPUE.REASON_CODE, fecCPUE.FE_REASON_COMMENT, ",                    
                     "fecCPUE.GEAR_CODE,  fecCPUE.NS_AREA, ",
                     "fecCPUE.INSHORE_IND,      fecCPUE.SEAMOUNT_IND, fecCPUE.MAJOR_STAT_AREA_CODE, ",                
                     "fecCPUE.MINOR_STAT_AREA_CODE, fecCPUE.LOCALITY_CODE, ",                                   
                     "fecCPUE.FE_FISHING_Ground_COMMENT, ",
                     "fecCPUE.START_LATITUDE, fecCPUE.START_LONGITUDE, ",
                     "fecCPUE.END_LATITUDE, fecCPUE.END_LONGITUDE, ",
                     "fecCPUE.FE_BEGINNING_BOTTOM_DEPTH, fecCPUE.FE_END_BOTTOM_DEPTH, ",
                     "fecCPUE.FE_MODAL_BOTTOM_DEPTH, fecCPUE.TRAP_MODIFICATIONS_CODE, ",       
                     "fecCPUE.FE_USABILITY, fecCPUE.CPUE_SABLE_WEIGHT, ",
                     "fecCPUE.CPUE_SABLE_COUNT, fecCPUE.CPUE_TRAPS, fecCPUE.TOTAL_TRAPS, ",   
                     "ISNULL(fecCPUE.TOTAL_SABLE_COUNT, 0) AS TOTAL_SABLE_COUNT, ",
                     "ISNULL(fecCPUE.TOTAL_SABLE_WEIGHT, 0) AS TOTAL_SABLE_WEIGHT, ",
                     "fecCPUE.VERIFICATION_METHOD, fecCPUE.FE_START_LATTITUDE_DEGREE, ",
                     "fecCPUE.FE_START_LATTITUDE_MINUTE, fecCPUE.FE_START_LONGITUDE_DEGREE,",     
                     "fecCPUE.fe_start_longitude_minute, fecCPUE.FE_END_LATTITUDE_DEGREE, ", 
                     "fecCPUE.fe_end_lattitude_minute, fecCPUE.fe_end_longitude_degree,   ",
                     "fecCPUE.fe_end_longitude_minute, fecCPUE.START_FATHOMS, ",
                     "fecCPUE.END_FATHOMS, fecCPUE.MODAL_DEPTH_FM, ",
                     "fecCPUE.DepthStrataID, dbo.SurveyBlock_countWeight.nBlocks AS Nh, ",
                     "dbo.SurveyBlock_countWeight.Wh,", 
                     "ISNULL(fecCPUE.CPUE_SABLE_WEIGHT / NULLIF (fecCPUE.CPUE_TRAPS, 0), 0) AS cpue,",   
                     "dbo.GFBIO_RESEARCH_SAMPLE_DETAILS.[Proportion Males], ",
                     "dbo.GFBIO_RESEARCH_SAMPLE_DETAILS.[Male Mean Fork Len(mm)], ",
                     "dbo.GFBIO_RESEARCH_SAMPLE_DETAILS.[Female Mean Fork Len(mm)], ",                                        
                     "dbo.GFBIO_RESEARCH_SAMPLE_DETAILS.[Tagged Mean Fork Len(mm)]  ",
                     "from (select trp.TRIP_ID, trp.VESSEL_ID, trp.SUFFIX, trp.CAPTAIN_ID, fe_1.FISHING_EVENT_ID, ",
                     "fe_1.FE_MAJOR_LEVEL_ID, YEAR(dbo.SableSetDate(fe_1.fe_begin_deployment_time, ",
                     "fe_1.fe_end_deployment_time, fe_1.fe_begin_retrieval_time, ",
                     "fe_1.fe_end_retrieval_time)) AS SET_YEAR,  ",     
                     "MONTH(dbo.SableSetDate(fe_1.fe_begin_deployment_time, ",
                     "fe_1.fe_end_deployment_time, fe_1.fe_begin_retrieval_time, ",
                     "fe_1.fe_end_retrieval_time)) AS SET_MONTH,  ", 
                     "DAY(dbo.SableSetDate(fe_1.fe_begin_deployment_time, ",
                     "fe_1.fe_end_deployment_time, ",
                     "fe_1.fe_begin_retrieval_time, fe_1.fe_end_retrieval_time)) AS SET_DAY, ",
                     "CAST(DATEPART(hh, dbo.SableSetDate(fe_1.fe_begin_deployment_time, ",
                     "fe_1.fe_end_deployment_time, fe_1.fe_begin_retrieval_time, ",
                     "fe_1.fe_end_retrieval_time)) AS varchar) + ",
                     "CAST(DATEPART(mi, dbo.SableSetDate(fe_1.fe_begin_deployment_time, ",
                     "fe_1.fe_end_deployment_time, fe_1.fe_begin_retrieval_time, fe_1.fe_end_retrieval_time)) AS varchar) AS SET_TIME, ",
                     "DATEDIFF(mi, ISNULL(fe_1.fe_end_deployment_time, fe_1.fe_begin_deployment_time), ISNULL(fe_1.fe_begin_retrieval_time, ",  
                     "fe_1.fe_end_retrieval_time)) AS DURATION_MINUTES,  ",
                     "dbo.SableDepthGroup(fe_1.GROUPING_CODE) AS SABLE_DEPTH_GROUP, ",   
                     "dbo.SableAreaGroup(fe_1.GROUPING_CODE, fe_1.REASON_CODE, fe_1.FE_FISHING_Ground_COMMENT) AS SABLE_AREA_GROUP, ",
                     "dbo.SableSetType(fe_1.REASON_CODE,fe_1.FE_REASON_COMMENT, ISNULL(GFBioSQL.dbo.Dater(fe_1.fe_begin_deployment_time, ",  
                     "fe_1.fe_end_deployment_time, fe_1.fe_begin_retrieval_time, fe_1.fe_end_retrieval_time),  ",
                     "trp.TRIP_START_DATE)) AS SABLE_SET_TYPE, fe_1.GROUPING_CODE, fe_1.REASON_CODE, fe_1.FE_REASON_COMMENT, ",
                     "fe_1.GEAR_CODE, sloc.NS_AREA, sloc.INSHORE_IND, sloc.SEAMOUNT_IND, ",
                     "fe_1.MAJOR_STAT_AREA_CODE, fe_1.MINOR_STAT_AREA_CODE, fe_1.LOCALITY_CODE, fe_1.FE_FISHING_Ground_COMMENT, ",
                     "fe_1.FE_START_LATTITUDE_DEGREE + fe_1.FE_START_LATTITUDE_MINUTE / 60 AS START_LATITUDE, ",
                     "(fe_1.FE_START_LONGITUDE_DEGREE + fe_1.fe_start_longitude_minute / 60)  * - 1 AS START_LONGITUDE, ",
                     "fe_1.FE_END_LATTITUDE_DEGREE + fe_1.fe_end_lattitude_minute / 60 AS END_LATITUDE, ",
                     "(fe_1.fe_end_longitude_degree + fe_1.fe_end_longitude_minute / 60) * - 1 AS END_LONGITUDE, ",
                     "fe_1.FE_BEGINNING_BOTTOM_DEPTH, fe_1.FE_END_BOTTOM_DEPTH, fe_1.FE_MODAL_BOTTOM_DEPTH, ",
                     "fe_1.FE_MISC_COMMENT, fets.TRAP_MODIFICATIONS_CODE, fets.USABILITY_CODE AS FE_USABILITY, ",
                     "CAST(CASE WHEN fe_1.REASON_CODE <> 14 AND fets.USABILITY_CODE <> 13 THEN isnull(traps.CPUE_WEIGHT, ",
                     "CASE WHEN fets.USABILITY_CODE IN (1, 12) THEN CASE WHEN fec_1.catch_weight IS NULL AND ",
                     "isnull(fec_1.VERIFICATION_METHOD,0) <> 9 THEN 0 ELSE fec_1.catch_weight END ELSE NULL END)  ",
                     "else NULL end AS numeric(7,1)) ",
                     "AS CPUE_SABLE_WEIGHT, CAST(CASE WHEN fe_1.REASON_CODE <> 14 AND fets.USABILITY_CODE <> 13 THEN isnull(traps.CPUE_COUNT, ",
                     "CASE WHEN fets.USABILITY_CODE IN (1, 12) THEN CASE WHEN fec_1.catch_count IS NULL AND ",
                     "isnull(fec_1.VERIFICATION_METHOD, 0) <> 3 THEN 0 ELSE fec_1.catch_count END ELSE NULL END) ELSE NULL END ",
                     "AS smallint) AS CPUE_SABLE_COUNT, ",
                     "CAST(CASE WHEN fe_1.reason_code <> 14 AND fets.USABILITY_CODE <> 13 THEN ",
                     "isnull(CPUE_TRAPS, CASE WHEN fets.USABILITY_CODE IN (1, 12) THEN fets.TRAPS_FISHED_COUNT ELSE NULL END) ",
                     "ELSE NULL END AS smallint) AS CPUE_TRAPS, ISNULL(traps.TOTAL_TRAPS, fets.TRAPS_FISHED_COUNT) AS TOTAL_TRAPS, ",              
                     "CAST(ISNULL(traps.total_count, fec_1.CATCH_COUNT) AS smallint) as TOTAL_SABLE_COUNT, ",
                     "CAST(ISNULL(traps.total_weight, fec_1.CATCH_WEIGHT) AS numeric(7, 1)) AS TOTAL_SABLE_WEIGHT, ",
                     "fec_1.VERIFICATION_METHOD, fe_1.FE_START_LATTITUDE_DEGREE, fe_1.FE_START_LATTITUDE_MINUTE, ",
                     "fe_1.FE_START_LONGITUDE_DEGREE, fe_1.fe_start_longitude_minute, fe_1.FE_END_LATTITUDE_DEGREE, ",
                     "fe_1.fe_end_lattitude_minute, fe_1.fe_end_longitude_degree, fe_1.fe_end_longitude_minute, ",      
                     "round(PacHarvest.dbo.m2fa(fe_1.FE_BEGINNING_BOTTOM_DEPTH), 0) AS START_FATHOMS, ",
                     "round(PacHarvest.dbo.m2fa(fe_1.FE_END_BOTTOM_DEPTH), 0) AS END_FATHOMS, ",
                     "round(PacHarvest.dbo.m2fa(fe_1.FE_MODAL_BOTTOM_DEPTH), 0) AS MODAL_DEPTH_FM, ",
                     "dbo.DepthStrataID(round(fe_1.FE_MODAL_BOTTOM_DEPTH, 0), ",
                     "dbo.SableDepthGroup(fe_1.GROUPING_CODE)) AS DepthStrataID ",
                     "from GFBioSQL.dbo.TRIP AS trp INNER JOIN ",
                     "(select  TRIP_ID         ",
                     "from GFBioSQL.dbo.TRIP_ACTIVITY    ",
                     "where (ACTIVITY_CODE = 19)) AS act ON trp.TRIP_ID = act.TRIP_ID INNER JOIN  ",
                     "(select TRIP_ID,FISHING_EVENT_ID,FE_PARENT_EVENT_ID, ",
                     "FE_MAJOR_LEVEL_ID,FE_SUB_LEVEL_ID,FE_MINOR_LEVEL_ID,EMPLOYEE_ID, ",                                         
                     "fe_begin_deployment_time, fe_end_deployment_time, fe_begin_retrieval_time, fe_end_retrieval_time,  ",
                     "GROUPING_CODE, REASON_CODE, FE_REASON_COMMENT, MAJOR_STAT_AREA_CODE, ",
                     "MINOR_STAT_AREA_CODE, LOCALITY_CODE, DFO_STAT_AREA_CODE, DFO_STAT_SUBAREA_CODE, ",
                     "LOC_VRFN_METHOD_CODE, FE_FISHING_Ground_COMMENT, ",
                     "FE_START_LATTITUDE_DEGREE, FE_START_LATTITUDE_MINUTE,  ",
                     "FE_END_LATTITUDE_DEGREE,   fe_end_lattitude_minute,      ",             
                     "FE_START_LONGITUDE_DEGREE, fe_start_longitude_minute,     ",
                     "fe_end_longitude_degree, fe_end_longitude_minute, ",
                     "FE_START_LORAN_X, FE_START_LORAN_Y, FE_END_LORAN_X, FE_END_LORAN_Y, ",
                     "FE_DISTANCE_TRAVELLED, FE_DIRECTION_OF_SET, FE_PLOTTER_RECORD_INFOR, ",
                     "DEPTH_VRFN_METHOD_CODE, FE_BEGINNING_BOTTOM_DEPTH, FE_END_BOTTOM_DEPTH,  ",
                     "FE_MODAL_BOTTOM_DEPTH, FE_MIN_BOTTOM_DEPTH, FE_MAX_BOTTOM_DEPTH,  ",
                     "FE_BEGIN_TARGET_DEPTH, FE_END_TARGET_DEPTH, FE_MIN_TARGET_DEPTH, FE_MAX_TARGET_DEPTH,  ",
                     "FE_MODAL_TARGET_DEPTH, FE_BEGIN_CAPTURE_DEPTH, FE_END_CAPTURE_DEPTH,  ",
                     "FE_MIN_CAPTURE_DEPTH, FE_MAX_CAPTURE_DEPTH, FE_MODAL_CAPTURE_DEPTH,  ",
                     "FE_BEGINNING_GEAR_DEPTH, FE_END_GEAR_DEPTH, FE_MIN_GEAR_DEPTH, FE_MAX_GEAR_DEPTH, FE_MODAL_GEAR_DEPTH,  ",  
                     "FE_SURFACE_WATER_TEMPERATURE,  ",
                     "FE_SURFACE_WATER_TEMP_DEPTH, FE_SURFC_WATR_TEMP_TECH_CODE, FE_BOTTOM_WATER_TEMPERATURE,  ",
                     "FE_BOTTOM_WATER_TEMP_DEPTH, FE_BOTTM_WATR_TEMP_TECH_CODE,  ",
                     "FE_MODAL_DEPTH_TEMPERATURE, FE_GEAR_TEMP_TECH_CODE, FE_CTD_REF_NUMBER,  ",
                     "FE_WIND_DIRECTION, FE_WIND_SPEED, BEAUFORT_SCALE_CODE, FE_SWELL, TIDE_CODE,  ",
                     "FE_CLOUD_COVER, FE_LUMINESCENCE, FE_WEATHER_COMMENT, FE_SUN_SHINING_IND, GEAR_CODE,  ",   
                     "EST_CATCH_METHOD_CODE, FE_TOTAL_CATCH_WEIGHT, FE_TOTAL_CATCH_PIECES,  ",
                     "FE_CATCH_WEIGHT_PER_PIECE, FE_SOUNDER_COMMENT, FE_EK500_TAPE_NUMBER,  ",
                     "FE_MISC_COMMENT, ROW_VERSION, BLOCK_DESIGNATION, FE_BEGIN_BOTTOM_CONTACT_TIME,  ",
                     "FE_END_BOTTOM_CONTACT_TIME, BOTTOM_CONTACT_METHOD_CODE, MODIFIED_DATE, MODIFIED_BY,  ",
                     "HAUL_RECORDER, FE_CATCH_COMMENT, PARTIAL_SORT_IND,  ",
                     "FE_CATCH_VERIFICATION_COMMENT, SCALE_ID, CAPTAIN_ID ",
                     "from GFBioSQL.dbo.FISHING_EVENT ",
                     "where (FE_PARENT_EVENT_ID IS NULL)) AS fe_1 ON trp.TRIP_ID = fe_1.TRIP_ID LEFT OUTER JOIN dbo.traps AS traps ",
                     "ON fe_1.TRIP_ID = traps.TRIP_ID AND fe_1.FE_MAJOR_LEVEL_ID = traps.FE_MAJOR_LEVEL_ID LEFT OUTER JOIN ",
                     "dbo.sablefish_locality AS sloc ON fe_1.MAJOR_STAT_AREA_CODE = sloc.MAJOR_STAT_AREA_CODE  ",
                     "and fe_1.MINOR_STAT_AREA_CODE = sloc.MINOR_STAT_AREA_CODE AND  ",
                     "fe_1.LOCALITY_CODE = sloc.LOCALITY_CODE LEFT OUTER JOIN ",
                     "GFBioSQL.dbo.TRAP_SPECS AS fets ON fe_1.FISHING_EVENT_ID = fets.FISHING_EVENT_ID LEFT OUTER JOIN ",
                     "(select  fec.FISHING_EVENT_ID, CATCH_1.SPECIES_CODE, SUM(CATCH_1.CATCH_WEIGHT) AS CATCH_WEIGHT,  ",
                     "sum(CATCH_1.CATCH_COUNT) AS CATCH_COUNT, AVG(ISNULL(CATCH_1.CATCH_VERIFICATION_CODE, 0)) AS VERIFICATION_METHOD ",
                     "from GFBioSQL.dbo.FISHING_EVENT_CATCH AS fec INNER JOIN ",                                                                  
                     "GFBioSQL.dbo.CATCH AS CATCH_1 ON fec.CATCH_ID = CATCH_1.CATCH_ID ",
                     "where (CATCH_1.SPECIES_CODE = '455') ",
                     "group by fec.FISHING_EVENT_ID, CATCH_1.SPECIES_CODE) AS fec_1 ON fe_1.FISHING_EVENT_ID = fec_1.FISHING_EVENT_ID ", 
                     "where (YEAR(dbo.SableSetDate(fe_1.fe_begin_deployment_time, fe_1.fe_end_deployment_time,  ",
                     "fe_1.fe_begin_retrieval_time, fe_1.fe_end_retrieval_time)) > 2002))  AS fecCPUE LEFT OUTER JOIN ",
                     "dbo.GFBIO_RESEARCH_SAMPLE_DETAILS ON fecCPUE.FE_MAJOR_LEVEL_ID = dbo.GFBIO_RESEARCH_SAMPLE_DETAILS.[SET] AND  ",
                     "fecCPUE.TRIP_ID = dbo.GFBIO_RESEARCH_SAMPLE_DETAILS.TRIP_ID LEFT OUTER JOIN ",
                     "dbo.SurveyBlock_countWeight ON fecCPUE.SABLE_AREA_GROUP = dbo.SurveyBlock_countWeight.areaStrName AND   ",      
                     "fecCPUE.DepthStrataID = dbo.SurveyBlock_countWeight.depthStrName", sep="")

    #raw_survey_data<- GetSQLData(landmrk,"Sablefish")
    #write.table(raw_survey_data, file = paste(path,"figure567.csv",sep=''),row.names=FALSE, na="",col.names=TRUE,  sep=",")
    raw_survey_data <- read.csv(paste(path,'figure567.csv',sep=''),header=T)
    #raw_survey_data <- raw_survey_data[raw_survey_data$SET_YEAR<2013,]
    
    # load survey data 
    library(Rmisc)
    strs01            <- subset(raw_survey_data,SABLE_SET_TYPE=="StRS") 
    strs01$sable_cpue <- strs01$CPUE_SABLE_WEIGHT/strs01$CPUE_TRAPS           # changed from TOTAL_TRAPS to CPUE_TRAPS
    strs01$sable_cnts <- strs01$CPUE_SABLE_COUNT/strs01$CPUE_TRAPS 
    strs01$sable_wt   <- strs01$CPUE_SABLE_WEIGHT/strs01$CPUE_SABLE_COUNT
    strs01$strata     <- paste(strs01$SABLE_AREA_GROUP,strs01$SABLE_DEPTH_GROUP)
    strs02            <- arrange(transform(strs01,strata=factor(strata,levels=rev(unique(strs01$strata)))),strata)
    tgc01             <- summarySE(strs02, measurevar="sable_cpue", groupvars=c("SET_YEAR","strata"),na.rm = T)
    tgc.02            <- arrange(transform(tgc01,strata=factor(strata,levels = c("S5 RD3", "S5 RD2", "S5 RD1", 
                                                                                 "S4 RD3", "S4 RD2", "S4 RD1", 
                                                                                 "S3 RD3", "S3 RD2", "S3 RD1", 
                                                                                 "S2 RD3", "S2 RD2", "S2 RD1",
                                                                                 "S1 RD3", "S1 RD2", "S1 RD1" ))),strata)
  
     # drop 2003 and 2004 and set panel ordering for aesthetics
     strs.02<-arrange(transform(strs01[strs01$SET_YEAR>2002 & strs01$SET_YEAR<2013,],
                                SET_YEAR=factor(SET_YEAR,levels=c(2003,2006,2009,2011,
                                                                  2004,2007,2010,2012,
                                                                  2005,2008
                                                                  ))),SET_YEAR)
    
   # ggplot( strs.02,aes(x=FE_MODAL_BOTTOM_DEPTH,y=CPUE_SABLE_WEIGHT/CPUE_TRAPS))+
   #         geom_point(alpha = 3/5,color="steelblue")+
   #         facet_wrap(~SET_YEAR,ncol=4)+
   #         scale_x_continuous(breaks = c(100,450,850,1400),limits=c(0,1500))+ 
   #         geom_vline(xintercept=c(450),linetype="dashed",color="steelblue")+
   #         geom_vline(xintercept=c(850),linetype="dashed",color="steelblue")+
   #         xlab("Depth (m)")+
   #         ylab("CPUE (kg/trap)")+
    #        theme_bw()

```
\clearpage
(ref:figure6) Average sablefish catch per unit effort (CPUE; mean +/- 95% CIs) by survey strata since 2003. Panels run deep to shallow (left to right) and north to south (top to bottom).

```{r figure6, fig.cap='(ref:figure6)', out.width = "450px", out.height = "576px",echo=FALSE, fig.align="center", warning=FALSE}

     png(paste(basepath,'figure6.png',sep=''), width=500, height=641) # write png to file
     par(mfcol=c(1,1))
     tgc.02 <- tgc.02[tgc.02$SET_YEAR<2013,]
     tgc.02$col <- ifelse(tgc.02$SET_YEAR == 2012, "red", "steelblue")
     
     integer_breaks <- function(n = 5, ...) {
          fxn <- function(x) {
               breaks <- floor(pretty(x, n, ...))
               names(breaks) <- attr(breaks, "labels")
               breaks
           }
      return(fxn)
      } 

     ggplot(tgc.02,aes(x=SET_YEAR,y=sable_cpue,label = round(sable_cpue,0))) +
       geom_text(size = 3, vjust = 0, nudge_y = 1.5) +
     geom_errorbar(aes(ymin=sable_cpue-ci, ymax=sable_cpue+ci), width=0, col=tgc.02$col) +
     geom_line(col=tgc.02$col) +
     geom_point(col=tgc.02$col) +
     facet_wrap(~strata,nrow=5)+
     xlab("Year")+
     ylab("Mean CPUE (kg/trap)") +
     scale_x_continuous(breaks = integer_breaks()) +
     theme(     panel.background =  element_rect(fill = "white",
                                    colour = "grey50",
                                    size = 0.5, linetype = "solid"),
                panel.grid.major =  element_line(size = 0.5, linetype = 'solid',
                                    colour = "grey90"), 
                panel.grid.minor =  element_line(size = 0.25, linetype = 'solid',
                                    colour = "grey90"),
                strip.background =  element_rect(fill = "grey80", colour = "grey30"), 
                plot.margin=unit(c(0.2,0.2,0.2,1),"cm")) 
     
  
     while (!is.null(dev.list()))  dev.off()
     img <-   paste(basepath,'figure6.png',sep='')   # -- retrieve png 
              knitr::include_graphics(img)
```
\clearpage
(ref:figure7) Average number of sablefish per trap (mean +/- 95% CIs) by StRS survey strata over time. Panels run deep to shallow (left to right) and north to south (top to bottom).

```{r figure7, fig.cap='(ref:figure7)', out.width = "450px", out.height = "576px",echo=FALSE, fig.align="center", warning=FALSE}

    png(paste(basepath,'figure7.png', sep=''), width=500, height=641) # write png to file
    par(mfcol=c(1,1))
    
    raw_survey_data        <- raw_survey_data[raw_survey_data$SET_YEAR<2013,]
    strs                   <- subset(raw_survey_data,SABLE_SET_TYPE=="StRS") 
    strs$sable_cpue        <- strs$CPUE_SABLE_WEIGHT/strs$CPUE_TRAPS 
    strs$sable_cnt         <- (strs$CPUE_SABLE_COUNT/strs$CPUE_TRAPS)
    strs$sable_wg          <- (strs$CPUE_SABLE_WEIGHT/strs$CPUE_SABLE_COUNT) 
    strs$sable_avwt_trap   <- (strs$sable_cpue/strs$sable_cnt)
    strs$strata            <-  paste(strs$SABLE_AREA_GROUP,strs$SABLE_DEPTH_GROUP)
 
    strs2 <- arrange(transform(strs,strata=factor(strata,levels=rev(unique(strs$strata)))),strata)
    
    tgc   <- summarySE(strs2, measurevar=("sable_cpue"),         groupvars=c("SET_YEAR","strata"),na.rm = T)
    tgcwg <- summarySE(strs2, measurevar=("sable_wg"),           groupvars=c("SET_YEAR","strata"),na.rm = T)
    tgcnt <- summarySE(strs2, measurevar=("sable_cnt"),          groupvars=c("SET_YEAR","strata"),na.rm = T)

    tgc   <- arrange(transform(tgc,
                     strata=factor(strata,
                                   levels=c("S5 RD3", "S5 RD2", "S5 RD1", 
                                            "S4 RD3", "S4 RD2", "S4 RD1", 
                                            "S3 RD3", "S3 RD2", "S3 RD1", 
                                            "S2 RD3", "S2 RD2", "S2 RD1",
                                            "S1 RD3", "S1 RD2", "S1 RD1"))),strata)
    
    tgcwg<-arrange(transform(tgcwg,
                             strata=factor(strata,
                                           levels=c("S5 RD3", "S5 RD2", "S5 RD1", 
                                                    "S4 RD3", "S4 RD2", "S4 RD1", 
                                                    "S3 RD3", "S3 RD2", "S3 RD1", 
                                                    "S2 RD3", "S2 RD2", "S2 RD1",
                                                    "S1 RD3", "S1 RD2", "S1 RD1"))),strata)
    
    tgcnt<-arrange(transform(tgcnt,
                             strata=factor(strata,
                                           levels=c("S5 RD3", "S5 RD2", "S5 RD1", 
                                                    "S4 RD3", "S4 RD2", "S4 RD1", 
                                                    "S3 RD3", "S3 RD2", "S3 RD1", 
                                                    "S2 RD3", "S2 RD2", "S2 RD1",
                                                    "S1 RD3", "S1 RD2", "S1 RD1"))),strata)

    tgcnt$col <- ifelse(tgcnt$SET_YEAR == 2012, "red", "steelblue")
    ggplot(tgcnt,aes(x=SET_YEAR,y=sable_cnt, label= round(sable_cnt,0))) +
      geom_text(size = 3, vjust = 0, nudge_y = 1.5) +
           geom_errorbar(aes(ymin=sable_cnt-ci, ymax=sable_cnt+ci), width=0, col=tgcnt$col) +
           geom_line(col=tgcnt$col) +
           geom_point(col=tgcnt$col) +
           facet_wrap(~rev(strata),nrow=5,labeller = )+
           coord_cartesian(ylim=c(0,40))+ 
           xlab("Year")+
           ylab("Mean CPUE (#fish/trap)")+
           scale_x_continuous(breaks = integer_breaks()) +
        
     theme(panel.background = element_rect(fill = "white",
                              colour = "grey50",
                              size = 0.5, linetype = "solid"),
           panel.grid.major = element_line(size = 0.5, linetype = 'solid',
                              colour = "grey90"), 
           panel.grid.minor = element_line(size = 0.25, linetype = 'solid',
                              colour = "grey90"),
           strip.background = element_rect(fill = "grey80", colour = "grey30"), 
           plot.margin=unit(c(0.2,0.2,0.2,1),"cm")) 
    
    while (!is.null(dev.list()))  dev.off()
    img <- paste(basepath,'figure7.png',sep='')   # -- retrieve png 
           knitr::include_graphics(img)
    
```
\clearpage
(ref:figure8) Average weight of sablefish (mean +/- 95% CIs) by survey strata over time. Panels run deep to shallow (left to right) and north to south (top to bottom).  Points in black specify weights > 3.5 kg.

```{r figure8, fig.cap='(ref:figure8)', out.width = "450px", out.height = "576px",echo=FALSE, fig.align="center", warning=FALSE}

    png(paste(basepath,'figure8.png',sep=''),width=500, height=641) # write png to file
    par(mfcol=c(1,1))
    tgcwg$col  <- ifelse(tgcwg$SET_YEAR == 2012, "red", "steelblue")
    tgcwg$col2 <- ifelse(tgcwg$sable_wg >= 3.6, "black", "steelblue")
    
    tgcwg <- tgcwg[tgcwg$SET_YEAR<2013,]

    ggplot(tgcwg,aes(x= SET_YEAR, y=sable_wg, label= round(sable_wg,1))) +
      geom_text(size = 3, vjust = 0, nudge_y = -1.1) +
    geom_errorbar(aes(ymin=sable_wg-ci, ymax=sable_wg+ci), width=0, col=tgcwg$col) +
    geom_line(col=tgcwg$col) +
    geom_point(col=tgcwg$col) +
    geom_point(col=tgcwg$col2) +  
    facet_wrap(~strata,nrow=5)+
    coord_cartesian(ylim=c(1,6)) + 
    xlab("Year")+
    ylab("Sablefish weight (kg)") +
             scale_x_continuous(breaks = integer_breaks()) +
     theme(     panel.background = element_rect(fill = "white",
                                colour = "grey50",
                                size = 0.5, linetype = "solid"),
                panel.grid.major = element_line(size = 0.5, linetype = 'solid',
                                colour = "grey90"), 
                panel.grid.minor = element_line(size = 0.25, linetype = 'solid',
                                colour = "grey90"),
                strip.background =  element_rect(fill = "grey80", colour = "grey30"), 
                plot.margin=unit(c(0.2,0.2,0.2,1),"cm")) 
    
    while (!is.null(dev.list()))  dev.off()
    img <-    paste(basepath,'figure8.png',sep='')   # -- retrieve png 
              knitr::include_graphics(img)
```   
\clearpage
(ref:figure9) Annual mean weight of sablefish per trap (kg/trap) (A);  annual mean number of sablefish per trap (#fish/trap) (B); annual mean weight of sablefish (kg) (C) by StRS survey strata over time. Horizontal line is median and blue dots are arithmetic mean.

```{r figure9, fig.cap='(ref:figure9)', out.width = "450px", out.height = "576px",echo=FALSE, fig.align="center", warning=FALSE}

  png(paste(basepath,'figure9.png', sep=''), width=600, height=800) # write png to file
  library(cowplot)
       tgc <- tgc[tgc$SET_YEAR<2013,]
       
       p <- ggplot(tgc,aes(x=as.factor(SET_YEAR),y=sable_cpue)) + 
          geom_boxplot(fill="grey90", width=0.5) +
          stat_summary(fun.y=mean, geom="point", shape=16, size=2,col="steel blue")+
          stat_summary(fun = mean, geom = "text", col = "red", size=4.5,    # Add text to plot
                       vjust = 2.0, aes(label = paste("", round(..y.., digits = 1)))) +
          stat_summary(fun.y=mean, geom="point", shape=16, size=2,col="steelblue") +
          xlab("Year")+
          ylab("StRS CPUE (kg/trap)")+
          #scale_y_continuous(limits=c(0,175))+
           scale_x_discrete(breaks = seq(2003, 2012, by = 1)) +
                 annotate(geom="text", x=8, y=60, label="StRS",
                 color="steel blue", size=5) +
          theme(axis.text = element_text(size = 6)) + 
          theme_bw()
       
       p1 <- ggplot(tgcnt, aes(x=as.factor(SET_YEAR), y=sable_cnt)) + 
          geom_boxplot(fill="grey90", width=0.5) +
          stat_summary(fun.y=mean, geom="point", shape=16, size=2,col="steelblue")+
                   stat_summary(fun = mean, geom = "text", col = "red", size=4.5,    # Add text to plot
                       vjust = 2.0, aes(label = paste("", round(..y.., digits = 1)))) +
          xlab("Year") +
          ylab("CPUE (#fish/trap)") +
          #scale_y_continuous(limits=c(0,75))+
          theme(axis.text = element_text(size = 6)) + 
          theme_bw()
     
     p2 <-ggplot(tgcwg, aes(x=as.factor(SET_YEAR), y=sable_wg )) + 
          geom_boxplot(fill="grey90", width=0.5) +
          stat_summary(fun.y=mean, geom="point", shape=16, size=2,col="steelblue")+
                 stat_summary(fun = mean, geom = "text", col = "red", size=4.5,    # Add text to plot
                       vjust = 2.0, aes(label = paste("", round(..y.., digits = 1)))) +
          xlab("Year") +
          ylab("Mean weight (kg)") +
          theme(axis.text = element_text(size = 6)) + 
          theme_bw()

    plot_grid(p, p1, p2, labels = "AUTO", nrow = 3)    
  
    while (!is.null(dev.list()))  dev.off()
    img <-    paste(basepath,'figure9.png',sep="")   # -- retrieve png 
              knitr::include_graphics(img)

```
\clearpage

(ref:figure10) Average weight of sablefish per trap (kg/trap) (A);  average number of sablefish per trap (#fish/trap) (B); annual average weight of sablefish (kg) (C) at mainland inlets over time.  Horizontal line is median and blue dots are arithmetic mean.

```{r figure10, fig.cap='(ref:figure10)', results='asis', out.width = "450px",out.height = "560px", fig.align="center"}

    png(paste(basepath,'figure10.png',sep=''), width=600, height=800) # write png to file

    library(Rmisc)                       
    cpuedt    <-  "SELECT  * from dbo.GENERIC_GFBIO_TRAPS where year < 2013 and [Spatial.Stratum] not like '%Quatsino Sound%' "
    #cpuedat   <-  GetSQLData(cpuedt,"Sablefish") 
    #write.table(cpuedat, file = paste(path,"figure10.csv",sep=''),row.names=FALSE, na="",col.names=TRUE, sep=",")
    cpuedat   <-  read.csv(paste(path,'figure10.csv',sep=''),header=T)


    #pick out the stand sets
    dat   <- cpuedat[ which(cpuedat$SABLE.SET.TYPE=="INLET STANDARDIZED" ), ]
    dat   <- dat[ which(is.na(dat$SABLE.SET.TYPE)==FALSE), ]
    inlet <- dat[dat$year >1993 & dat$year <=2012,]  
    
    inlet$sable_cpuew <-  inlet$CPUE.SABLE.WEIGHT/inlet$CPUE.TRAPS
    itgcw             <-  summarySE(inlet, measurevar="sable_cpuew", groupvars=c("year"),na.rm = T) 
    
    inlet.2w          <-  arrange(transform(inlet[inlet$year>1993,],year=factor(year,levels=c(1994,1995,1996,1997,
                                                                                              1998,1999,2000,2001,
                                                                                              2002,2003,2004,2005,
                                                                                              2006,2007,2008,2009,
                                                                                              2010,2011,2012))),year)

    inlet$sable_cpue  <-  inlet$CPUE.SABLE.COUNT/inlet$CPUE.TRAPS
    itgc              <-  summarySE(inlet, measurevar="sable_cpue", groupvars=c("year"),na.rm = T) 
    inlet.2           <-  arrange(transform(inlet[inlet$year>1993,],year=factor(year,levels=c(1994,1995,1996,1997,
                                                                                              1998,1999,2000,2001,
                                                                                              2002,2003,2004,2005,
                                                                                              2006,2007,2008,2009,
                                                                                              2010,2011,2012))),year)
    inlet$sable_cpuwg <-  inlet$CPUE.SABLE.WEIGHT/inlet$CPUE.SABLE.COUNT
    itgcwg            <-  summarySE(inlet, measurevar="sable_cpuwg", groupvars=c("year"),na.rm = T) 
    inlet.2wg         <-  arrange(transform(inlet[inlet$year>1993,],year=factor(year,levels=c(1994,1995,1996,1997,
                                                                                              1998,1999,2000,2001,
                                                                                              2002,2003,2004,2005,
                                                                                              2006,2007,2008,2009,
                                                                                              2010,2011,2012))),year)
    

     p <- ggplot(inlet.2w, aes(x=year, y=CPUE.SABLE.WEIGHT/CPUE.TRAPS)) +
          geom_boxplot(fill="grey90", width=0.4) +
          stat_summary(fun.y=mean, geom="point", shape=16, size=2,col="steel blue")+
                         stat_summary(fun = mean, geom = "text", col = "red", size=4.5,    # Add text to plot
                       vjust = 2.0, aes(label = paste("", round(..y.., digits = 1)))) +
          xlab("Year") +
          ylab("CPUE (kg/trap)") +
          #scale_y_continuous(limits=c(0,100))+
          scale_x_discrete(breaks = seq(1994, 2012, by = 2)) +
                 annotate(geom="text", x=14, y=90, label="Mainland inlets",
                 color="steel blue", size=5) +
          theme(axis.text = element_text(size = 5)) + 
          theme_bw()
    
     
     p1 <- ggplot(inlet.2, aes(x=year, y=CPUE.SABLE.COUNT/CPUE.TRAPS),
                          position =  position_dodge2(width = 0.5, preserve = "single")) + 
          geom_boxplot(fill="grey90", width=0.4) +
          stat_summary(fun.y=mean, geom="point", shape=16, size=2,col="steel blue")+
                         stat_summary(fun = mean, geom = "text", col = "red", size=4.5,    # Add text to plot
                       vjust = 2.0, aes(label = paste("", round(..y.., digits = 1)))) +
          xlab("Year") +
          ylab("CPUE (#fish/trap)") +
          #scale_y_continuous(limits=c(0,100))+
          scale_x_discrete(breaks = seq(1994, 2012, by = 2)) +
          theme(axis.text = element_text(size = 5)) + 
          theme_bw()
     
     p2 <- ggplot(inlet.2wg, aes(x=year, y=CPUE.SABLE.WEIGHT/CPUE.SABLE.COUNT),
                          position =  position_dodge2(width = 0.5, preserve = "single")) + 
          geom_boxplot(fill="grey90", width=0.4) +
          stat_summary(fun.y=mean, geom="point", shape=16, size=2,col="steel blue")+
                         stat_summary(fun = mean, geom = "text", col = "red", size=4.5,    # Add text to plot
                       vjust = 2.0, aes(label = paste("", round(..y.., digits = 1)))) +
          xlab("Year") +
          ylab("Mean weight (kg)") +
          theme(axis.text = element_text(size = 2)) + 
          scale_x_discrete(breaks = seq(1994, 2012, by = 2)) +
          theme_bw()
     
     plot_grid(p, p1, p2, labels = "AUTO", nrow = 3)

     while (!is.null(dev.list()))  dev.off()
     img <-  paste(paste(basepath,'figure10.png',sep=""))   # -- retrieve png 
          knitr::include_graphics(img)

```

\clearpage

(ref:figure11) Length frequencies for female (cyan) and male sablefish (green) and up to `r yr+1` for all StRS sets.  The number of specimens is denoted by the letter n, the mean indicated by the xbar $\overline{x}$ and the standard deviation is represented by the symbol sigma $\sigma$ (A). Average length and ratios of male and female sablefish by year. Counts by sex are shown across the top of the lines (B).

```{r figure11, fig.cap='(ref:figure11)',results='asis', out.width = "450px",out.height = "550px", fig.align="center"}

      knitr::opts_chunk$set(out.height = "\\textheight",  out.width = "\\textwidth")
      #  L E N G T H    H I S T O G R A M  
      #  Sablefish.dbo.procReport_Survey_LenMF pulls length data from table GFBIO_SABLEBIO_VW 
      #  procedure:  Build_BIO_Sablefish_Tables 
   
      png(paste(basepath,'figure11.png',sep=""), width = 800, height = 924) # write png to folder
      
      par(mfcol=c(2,1), mar=c(4,4,1,1), oma=c(3,2,1,1), cex=1.2)  # -- mar(bottom, left, top, and right)
      par(xpd=NA)  # for placement of A,B
     	a2    <-   hist(females, breaks = brk, plot=F)
    	b2    <-   hist(males,   breaks = brk, plot=F)  # draw the histogram with the specified number of bins
    	
 	    plot(b2, col=rgb(0.27,.51,.71,0.5), border="white", main="", xlab="Length (cm)", xlim=c(30,100))
    	plot(a2, col=rgb(0.1,0.1,0.1,0.5),  border="white", add = TRUE)
    	box()
    	
      panLab(0.79,0.4,paste("StRS 2003-", yr, sep=""), cex=1.2)  # -- Labels
    	panLab(0.19,0.98,"Sablefish males", col="steel blue")
    	panLab(0.79,0.98,"Sablefish females", col= "gray50")
    	
    	panLab(0.19,0.9,bquote(bold(n)==.(tm)))
    	panLab(0.79,0.9,bquote(bold(n)==.(tf)))
    	
    	panLab(0.19,0.8,bquote(bolditalic(bar(x))==.(mLm)))
    	panLab(0.79,0.8,bquote(bolditalic(bar(x))==.(mLf)))
    	
    	panLab(0.19,0.7,bquote(bold(sigma)==.(stdm)) )
    	panLab(0.79,0.7,bquote(bold(sigma)==.(stdf)) )
    	
    	 di <- dev.size("in")
       x  <- grconvertX(c(0, di[1]), from="in", to="user")
       y  <- grconvertY(c(0, di[2]), from="in", to="user")
       fig <- par("fig")
       x <- x[1] + (x[2] - x[1]) * fig[1:2]
       y <- y[1] + (y[2] - y[1]) * fig[3:4]
       txt <- "A"
       x <- x[1] + strwidth(txt, cex=3) / 2
       y <- y[2] - strheight(txt, cex=3)/ 2
       text(x, y, txt, cex=1.5)

     #  M E A N   L E N G T H   P L O T 
     #  Sablefish.dbo.rocRReport_Survey_LenAvg pulls length data from table GFBIO_SABLEBIO_VW from 
     #  procedure:  Build_BIO_Sablefish_Tables
     
     lenstats  <- "exec procRReport_Survey_LenAvg"
     #dat       <- GetSQLData(lenstats,"Sablefish") 
     #write.table(dat, file = paste(path,"figure11.csv",sep=''),row.names=FALSE, na="",col.names=TRUE,  sep=",")
     dat       <- read.csv(paste(path,'figure11.csv', sep=''),header=T) # read from csv
     dat       <- dat[dat$YEAR <= yr, ]
     
     fdat      <- dat[dat$sex==2,]
     mdat      <- dat[dat$sex==1,]
     #format(fdat$count/(fdat$count+mdat$count),digits=2)
     #format(mdat$count/(fdat$count+mdat$count),digits=2)
     MxSeam    <- max(dat$AvL)
    
     plot(fdat$YEAR, fdat$AvL,pch=2, ylim=c(50,MxSeam+5),xlim=c(2003,yr), cex=1.0, 
          ylab="Average length (cm)", xlab="Year", cex.lab=1.0, cex.axis = 1.0,
          col="gray30",xaxt="n")
     axis(1, seq(2003,2012,1), cex.axis=1.0)
     lines(fdat$YEAR,fdat$AvL,lwd=2, lty=2, col="gray30") # plot points and lines
     
     points(mdat$YEAR,mdat$AvL,pch=16,col="steelblue") 
     lines(mdat$YEAR, mdat$AvL,lwd=2,lty=1,col="steelblue")

     text(fdat$YEAR, fdat$AvL+1.5, fdat$count,cex=1.0)
     text(mdat$YEAR, mdat$AvL+1.5, mdat$count,cex=1.0)
     text(fdat$YEAR,53,format(mdat$count/fdat$count,digits=1),cex=1.0)
     text(2003.4,51,"M:F ratio",cex=1.0)
     par(usr=c(0,1,0,1))  # set up the plot margins
        
     legend(0.035,1, c("  Sablefish females","  Sablefish males"), 
            lty=c(2,1), lwd=2, bty="n", col=c("gray50","steelblue"), cex=1.0)
     legend(0.025,1, c("",""), pch=c(2,16), bty="n", col=c("gray50","steelblue"))
     #panLab(0.75,0.90,paste("StRS 2003-", yr, sep=""), cex=1.3)
     
       di <- dev.size("in")
       x  <- grconvertX(c(0, di[1]), from="in", to="user")
       y  <- grconvertY(c(0, di[2]), from="in", to="user")
       fig <- par("fig")
       x <- x[1] + (x[2] - x[1]) * fig[1:2]
       y <- y[1] + (y[2] - y[1]) * fig[3:4]
       txt <- "B"
       x <- x[1] + strwidth(txt, cex=3) / 2
       y <- y[2] - strheight(txt, cex=3)/ 2
       text(x, y, txt, cex=1.5)
     
     while (!is.null(dev.list()))  dev.off()  
     img6 <- paste(paste(basepath,'figure11.png',sep='')) 
            knitr::include_graphics(img6)
``` 
\clearpage
(ref:figure12) Sablefish fork length (L in cm) vs weight (W in kg) for females (A) and males (B) for the `r yr` survey.

```{r figure12, fig.cap='(ref:figure12)',results='asis', out.width = "480px", out.height = "282px", fig.align="center"}

    # Sablefish.dbo.procR_Survey_Sablefish_LenWt_shiny queries table GFBIO_SABLEBIO_VW for survey length data	
    png(paste(basepath,'figure12.png',sep=''), width = 700, height = 412) # -- starts writing a png to figure folder
    par(mfcol=c(1,2), mar=c(4,4,1,1), oma=c(2,2,3,1), cex=1.0)  # -- mar(bottom, left, top, and right)
    par(xpd=NA)  # for placement of A,B,C,D

    lenWT     <- "exec procR_Survey_Sablefish_LenWt_shiny"
    #lenWTdat1 <-  GetSQLData(lenWT,"Sablefish")                                                       # read from SQL Server
    #write.table(lenWTdat1, file = paste(path,"figure12.csv",sep=''),row.names=FALSE, na="",col.names=TRUE,  sep=",")    
    lenWTdat1 <- read.csv(paste(path,'figure12.csv',sep=''),header=T) # read from csv
    lenWTdat  <- lenWTdat1[lenWTdat1$YEAR==yr,]

    for (i in c(2,1)) {
         ylim <- c(min(lenWTdat$weight),max(lenWTdat$weight))
         xlim <- c(min(lenWTdat$length),max(lenWTdat$length))    
         lbls <- c(paste(yr,":  Males","",sep=""),paste(yr,":  Females","",sep=""))
   
         t    <- length(lenWTdat$length[lenWTdat$sex==i])                    
         fit1 <- lm(log(weight)~log(length), data=lenWTdat[lenWTdat$sex==i ,])
         a    <- round(exp(fit1$coef[1]),7)
         b    <- round(fit1$coef[2],3)
         Wt   <- (a * (0:xlim[2])^b)  

      plot(jitter(lenWTdat$length[lenWTdat$sex==i],2), 
           jitter(lenWTdat$weight[lenWTdat$sex==i],2), 
           pch=16, col="black", cex=0.5,
           xlab="     Fork length (cm)", ylab="   round weight (kg)", 
           main=paste(lbls[i]), xlim=c(0,100), ylim=c(0,12))      
           lines(0:xlim[2], Wt, col="steelblue", lwd=2) 
           
      mw     <- format(round(mean(lenWTdat$weight[lenWTdat$sex==i],na.rm=T),1),nsmall=1)
      par(usr=c(0,1,0,1))
      text(0.3,0.9, bquote(bold(n)==.(t)))   # -- number
      text(0.3,0.8, bquote(bolditalic(bar(W))==.(mw))) # -- mean weight
      text(0.33,0.7,bquote(bold(a)==.(a)))  # -- a
      text(0.32,0.6,bquote(bold(b)==.(b)))  # -- b
      
      letter <- c("B","A")
      di <- dev.size("in")
      x  <- grconvertX(c(0, di[1]), from="in", to="user")
      y  <- grconvertY(c(0, di[2]), from="in", to="user")
      fig <- par("fig")
      x <- x[1] + (x[2] - x[1]) * fig[1:2]
      y <- y[1] + (y[2] - y[1]) * fig[3:4]
      txt <- letter[i]
      x <- x[1] + strwidth(txt, cex=3) / 2
      y <- y[2] - strheight(txt, cex=3) *2
      text(x, y, txt, cex=1.5)
    }
    

   while (!is.null(dev.list()))  dev.off() 
   
   img <- paste(basepath,'figure12.png',sep='')
          knitr::include_graphics(img)
          
```
(ref:figure13) Bubble plot for female (A) and male (B) sablefish ages by survey year from StRS sets that have been aged.  The sizes of the circles are proportional to the number of fish with given ages. Fish age 35 and older are included in one bubble. The total number(n) of fish aged are listed across the top of each panel. The ages with the highest ratios are posted to the right of each bubble.

```{r figure13, fig.cap='(ref:figure13)',results='asis', out.width = "500px",out.height = "577px", fig.align="center"}

   # dt  <-  ("exec procRReport_Survey_proportions_at_age")  run this procedure to create table first.
   # sql server procedure:  procRReport_Survey_proportions_at_age which pulls age data from 
   # GFBIOSQL.dbo.b21_samples and b22_specimens

   png(paste(basepath,'figure13.png',sep=''), width = 800, height = 924)  # -- starts writing a png to figure folder

   dt   <-  paste("select * from Report_Survey_GFBIO_Age_MF_Prop where SetType='StRS' and Year<=", yr, sep="")
   #dat  <-  GetSQLData(dt,"Sablefish")                                                            # read from SQL Server
   #write.table(dat, file = paste(path,'figure13.csv',sep=''),row.names=FALSE, na="",col.names=TRUE,  sep=",")   
   dat  <-  read.csv(paste(path,'figure13.csv',sep=''),header=T) # read from csv

   par(mfrow=c(2,1),cex=1.1)     # -- two vertical plots
   par(xpd=NA)
   
   involve  <-  c()
   involve  <-  unique(dat$Year)
   maxyr    <-  max(involve)
   minyr    <-  min(involve)

   #  plot bubbles for female ages
   plot(dat$Year, dat$Age, type="n",
        xlab=" Year", ylab="", main="Females", 
        ylim=c(0,42), xlim=c(minyr,maxyr),xaxt="n")
        axis(1, seq(2003,2012,1))            
        symbols(dat$Year, dat$Age, 
                circles=pi*(dat$Female_Proportion),
                inches=0.3, add=T,col="light grey")

   for (femaleyr in involve)  # display totals across top
    {
    h <- unique(dat$Female_Yr_Total[dat$Year==femaleyr])
    text(femaleyr + 0.15, 40, bquote(.(h)))   
    text(femaleyr + 0.25, dat$Age[dat$f==1 & dat$Year==femaleyr],
         dat$Age[dat$f==1 & dat$Year==femaleyr],
         col="red",cex=1.1, font=2)
    }

    mtext(paste("Age","",sep=""), SOUTH<-2,  
          line=-1, adj=0.5, cex=1.2,  outer=TRUE)  # outside label
    
    di <- dev.size("in")
    x  <- grconvertX(c(0, di[1]), from="in", to="user")
    y  <- grconvertY(c(0, di[2]), from="in", to="user")
    fig <- par("fig")
    x <- x[1] + (x[2] - x[1]) * fig[1:2]
    y <- y[1] + (y[2] - y[1]) * fig[3:4]
    txt <- "A"   # label A
    x <- x[1] + strwidth(txt, cex=3) / 2
    y <- y[2] - strheight(txt, cex=3) / 2
    text(x, y, txt, cex=1.5)
    
       # plot bubbles for male ages
   plot(dat$Year, dat$Age, type="n", 
        xlab=" Year", ylab="", main="Males", 
        ylim=c(0,42), xlim=c(minyr,maxyr),
        xaxt="n")
        axis(1, seq(2003,2012,1))      
        symbols(dat$Year, dat$Age, 
                circles=pi*(dat$Male_Proportion),
                inches=0.3, add=T, col="light grey")

   for (maleyr in involve){
        h  <-  unique(dat$Male_Yr_Total[dat$Year==maleyr])
        text(maleyr + 0.15, 40, bquote(.(h)))    
        text(maleyr + 0.25, dat$Age[dat$m==1 & dat$Year==maleyr],
             dat$Age[dat$m==1 & dat$Year==maleyr],
             col="red",cex=1.1, font=2)}
   
        di <- dev.size("in")
        x  <- grconvertX(c(0, di[1]), from="in", to="user")
        y  <- grconvertY(c(0, di[2]), from="in", to="user")
        fig <- par("fig")
        x <- x[1] + (x[2] - x[1]) * fig[1:2]
        y <- y[1] + (y[2] - y[1]) * fig[3:4]
        txt <- "B"  # label B
        x <- x[1] + strwidth(txt, cex=3) / 2
        y <- y[2] - strheight(txt, cex=3) * 2
        text(x, y, txt, cex=1.5)
   
    while (!is.null(dev.list()))  dev.off()  
    img <-   paste(basepath,'figure13.png',sep='')   # retrieve png 
             knitr::include_graphics(img)
```
\clearpage

(ref:figure14) Coplot of average depth (m) vs average temperature ($^\circ$C) for a given 1-degree latitude range (blue bands) for `r yr`.  The number of fishing sets deployed with a SBE 39 recorder are represented by n.

```{r figure14, fig.cap='(ref:figure14)',results='asis', out.width = "500px",out.height = "335px", fig.align="center"}

      png(paste(basepath,'figure14.png',sep=''), width=920, height=424) # write png to file
      # table SEABIRD_ReportCoplot created in the Sablefish.dbo.Build_Seabird_tables procedure
      sbecp     <- paste("select * from SEABIRD_ReportCoplot where Year in(",yr,")",sep="")
      #ctddat    <- GetSQLData(sbecp,"Sablefish")   # read from SQL Server
      #write.table(ctddat, file = paste(path,"figure14.csv",sep=''),row.names=FALSE, na="",col.names=TRUE,  sep=",")      
      ctddat    <- read.csv(paste(path,'figure14.csv',sep=''),header=T)  # read from csv
      # View(ctddat)

      par(mar=c(1,1,1,1.4),cex=1.5,cex.lab=1.5, cex.axis=1.5, cex.main=1.5, cex.sub=1.5)   # par(mar=c(bottom,left,top,right) 
      yrdat     <-  ctddat[ctddat$Year==yr,]
      given.lat <-  matrix(c(48,48,49,49,50,50,51,51,52,52,53,53,54,54), 
                           nrow = 7, ncol=2, byrow=TRUE)
      
      coplot(temperature  ~ depth| lat, data = yrdat, 
             pch = 21, bg = "lightblue", col = "#0073C2FF",
             xlim=c(200,1400), 
             ylim=c(2,10),
             given.v = given.lat,
             show.given=FALSE, rows=1, cex=3.0, 
             xlab=c("Average Depth (m)",""),  
             ylab= expression(Average~Temperature~degree~C))

             n48 <- length(unique(yrdat$Sets[yrdat$lat == 48]))  # count number of sets in lat band
             n49 <- length(unique(yrdat$Sets[yrdat$lat == 49]))
             n50 <- length(unique(yrdat$Sets[yrdat$lat == 50]))
             n51 <- length(unique(yrdat$Sets[yrdat$lat == 51]))
             n52 <- length(unique(yrdat$Sets[yrdat$lat == 52]))
             n53 <- length(unique(yrdat$Sets[yrdat$lat == 53]))
             n54 <- length(unique(yrdat$Sets[yrdat$lat == 54]))

      labels   <-   c(n48,n49,n50,n51,n52,n53,n54)
      for(j in 1:7) 
         { text((280*j)-(100*(j-1)),8,paste("n=",labels[j],sep=""))  } 
      
      text(1350, 9, yr, font=2)  # make year bold = 2
      while (!is.null(dev.list()))  dev.off()

      require('magick')   # in order to stack images
      uno <- image_read(paste(basepath,'CoPlotTopMain.png', sep='')) # Read external images
      one <- image_read(paste(basepath,'figure14.png', sep=''))
      imgs = c(uno, one)
     
      # concatenate pngs left-to-right (use 'stack=T' to do it top-to-bottom)
      side_by_side = image_append(imgs, stack=T)
      image_write(side_by_side, path = paste(basepath,'figure14.png',sep=''), format = "png")  # save png

      img <-   paste(basepath,'figure14.png',sep='')   # retrieve png 
               knitr::include_graphics(img)

```
\clearpage
(ref:figure15) Vertical density ridgeplots of mean temperatures per year as reported by set from the Sea-bird SBE 39 loggers on traps at three depth intervals, RD~1~ = shallow (100-450 m), RD~2~ = mid (450-850 m), RD~3~ = deep (850-1400 m). Lines indicate the 2.5% and 97.5% tails.

```{r figure15, fig.cap='(ref:figure15)', results='asis', out.width = "440px",out.height = "500px", fig.align = "center"}

      # table SEABIRD_ReportLinePlot created  by Sablefish.dbo.Build_Seabird_tables procedure
    
      png(paste(basepath,'figure15.png',sep=''), width=600, height=700) # write png to file
      sea.bird     <-  "select * from SEABIRD_AverageTempPerSet where depth_stratum in('RD1','RD2','RD3')"
      #sea.bird.ridge    <-  GetSQLData(sea.bird,"Sablefish")   # read from SQL Server
      #write.table(sea.bird.ridge, file = paste(path,"figure15.csv",sep=''),row.names=FALSE, na="",col.names=TRUE,  sep=",") 
      sea.bird.ridge    <-  read.csv(paste(path,'figure15.csv',sep=''),header=T)  # read from csv
      sea.bird.ridge    <-  sea.bird.ridge[sea.bird.ridge$Year<= yr,]
      
      weather.raw2 <-    sea.bird.ridge[order(- sea.bird.ridge$Year,  sea.bird.ridge$Sets),]
      weather.raw2$years<-factor(weather.raw2$Year,levels=rev(unique(weather.raw2$Year)))
      names(weather.raw2) <- c("Year", "trip", "Sets", "Avgtemp", "Mintemp","Maxtemp", "Depth Stratum",  "lat", "years") 
      
      library(ggridges)
      
      #Median temperatures by year
      ggplot(weather.raw2, aes(x = Avgtemp, y = years, fill=`Depth Stratum`, alpha = 0.4)) +
             scale_x_continuous(limits = c(1.5,8.5)) +

             geom_density_ridges(
                aes(point_shape = `Depth Stratum`, alpha = 0.7), 
                alpha = .5, point_alpha = .8, jittered_points = TRUE
               ) +
             stat_density_ridges(quantile_lines = TRUE, quantiles = c(0.025, 0.975), alpha = 0.6) +
             xlab("Mean Temperature C") +
             ylab("Year") +
             theme_bw()
       
       while (!is.null(dev.list()))  dev.off()
       img <-   paste(basepath,'figure15.png',sep='')   # retrieve png 
                knitr::include_graphics(img)

```
\clearpage

(ref:figure16) Location of the vessel, accelerometer and the epicentre of a 7.7 magnitude earthquake on Saturday October 27, 2012 at 8:04 p.m.  Trap 15 accelerometer captured the earthquake event (inset).

```{r figure16, fig.cap='(ref:figure16)', out.width = "450px", out.height = "582px",echo=FALSE, fig.align="center", warning=FALSE}
      img  <- paste(basepath,'figure16.png',sep="") 
      knitr::include_graphics(img)
```
\clearpage


